Supporting Information for\\ ``Archaic introgression and the distribution of shared variation under stabilizing selection''

### 2024-08-19 doc/supplement.tex
paper edits

\title{Supporting Information}
\author{APR}
\date{\today}

@@

@@

\begin{figure}[ht!]
    \centering
    \includegraphics[width=0.6\textwidth]{../figures/underdominance.Ne_10000.s_-0.001.pdf}
    \caption{
        Comparison of predicted (\moments) and simulated SFS with underdominant
        selection. In this comparison, $N_e=10^4$ and $s=-1\times10^{-3}$, so that
        the population-size scale selection coefficient $\gamma=-20$.
        Simulations were performed under a Wright-Fisher model without linkage.
    }
    \label{fig:underdominance-validation-large-s}
\end{figure}

>>>>

\title{Supporting Information for\\
``Archaic introgression and the distribution
of shared variation under stabilizing selection''}
\author[]{Aaron P. Ragsdale}
\affil[]{Department of Integrative Biology, University of Wisconsin--Madison, WI, USA}
\date{\today}

@@

\begin{figure}[ht!]
    \centering
    \includegraphics{../figures/introgression_deserts.SD_0.05.pdf}
    \caption{
        Introgressed ancestry and probability of introgression deserts in and
        around functional regions, from simulations with high mutational variance.
        The demographic model is shown in Figure~\ref{fig:human-neand-h2}A.
    }
    \label{fig:deserts-high-VM}
\end{figure}

\begin{figure}[ht!]
    \centering
    \includegraphics{../figures/introgression_deserts.SD_0.01.pdf}
    \caption{
        Introgressed ancestry and probability of introgression deserts in and
        around functional regions, from simulations with moderate mutational variance.
        The demographic model is shown in Figure~\ref{fig:human-neand-h2}A.
    }
    \label{fig:deserts-med-VM}
\end{figure}

\begin{figure}[ht!]
    \centering
    \includegraphics{../figures/introgression_deserts.SD_0.005.pdf}
    \caption{
        Introgressed ancestry and probability of introgression deserts in and
        around functional regions, from simulations with low mutational variance.
        The demographic model is shown in Figure~\ref{fig:human-neand-h2}A.
    }
    \label{fig:deserts-low-VM}
\end{figure}

\begin{figure}[ht!]
    \centering
    \includegraphics{../figures/introgression_deserts.directional.mean_-0.0002.shape_0.5.pdf}
    \caption{
        Introgressed ancestry and probability of introgression deserts in and
        around functional regions, from simulations with directional selection.
        Deleterious mutations were drawn from a gamma distribution with mean
        $-0.0002$ and shape $0.05$.
        The demographic model is shown in Figure~\ref{fig:human-neand-h2}A.
    }
    \label{fig:deserts-directional-A}
\end{figure}

\begin{figure}[ht!]
    \centering
    \includegraphics{../figures/introgression_deserts.directional.mean_-0.001.shape_0.5.pdf}
    \caption{
        Introgressed ancestry and probability of introgression deserts in and
        around functional regions, from simulations with directional selection.
        Deleterious mutations were drawn from a gamma distribution with mean
        $-0.001$ and shape $0.05$.
        The demographic model is shown in Figure~\ref{fig:human-neand-h2}A.
    }
    \label{fig:deserts-directional-B}
\end{figure}

\begin{figure}[ht!]
    \centering
    \includegraphics[width=0.6\textwidth]{../figures/underdominance_F2.pdf}
    \caption{
        Underdominance, like negative selection, reduces expected $F_2$ compared
        to neutral divergence.
    }
    \label{fig:underdominance-F2}
\end{figure}

@@

\begin{figure}[ht!]
    \centering
    \includegraphics[width=0.6\textwidth]{../figures/underdominance.Ne_5000.s_-0.001.pdf}
    \caption{
        Comparison of predicted (\moments) and simulated SFS with underdominant
        selection. In this comparison, $N_e=5000$ and $s=-0.001$, so that
        the population-size scale selection coefficient $\gamma=-10$.
        Simulations were performed under a Wright-Fisher model without linkage.
    }
    \label{fig:underdominance-validation-large-s}
\end{figure}

\begin{figure}[ht!]
    \centering
    \includegraphics[width=0.6\textwidth]{../figures/underdominance.Ne_5000.s_0.0005.pdf}
    \caption{
        Comparison of predicted (\moments) and simulated SFS with \emph{over}dominant
        selection. In this comparison, $N_e=5000$ and $s=0.0005$, so that
        the population-size scale selection coefficient $\gamma=5$.
        Thus, with positive selection, heterozygotes are favored.
        Simulations were performed under a Wright-Fisher model without linkage.
    }
    \label{fig:overdominance-validation}
\end{figure}
